# Draft: Results


::: callout-note

Put your name on your work and give it an appropriate title -- edit your _quarto.yml file

:::

## Data

Data come from the BLS (Bureau of Labor Statistics) Survey of Occupational Injuries and
Illnesses (SOII), accessed through the IIF (Injuries, Illnesses, and Fatalities) database
[@IIFDatabasesUS]. Two tables are used: Table 1 reports total recordable case (TRC) rates 
the count of all recordable workplace injuries and illnesses per 100 full time equivalent
(FTE) workers by industry for 2024. Table R75 reports days away from work (DAFW) fall
rates, injuries serious enough to require at least one day off work, per 10,000 FTE workers 
by industry division for 2023–2024. Industries are classified using the North American
Industry Classification System (NAICS) as office or Non Office based on whether work is
primarily desk based.

::: callout-note
This should be in the data section, not the results section, but it looks good!

Make sure you add a date -- the release date? -- to your bibliography entry, and make sure the other fields are filled in. Zotero doesn't always catch everything perfectly.
:::

```{r}
#| label: setup
#| echo: false
#| message: false
#| warning: false

library(readxl)
library(knitr)
library(kableExtra)

# Read Table 1 - TRC rates by industry
t1 <- read_excel("Table1.xlsx", skip = 5, col_names = FALSE)
colnames(t1) <- c("Industry", "NAICS", "TRC", "DART", "DAFW", "DJTR", "Other")
t1$TRC <- suppressWarnings(as.numeric(t1$TRC))

# Read Table R75 - fall rates by industry division
r75 <- read_excel("TableR75.xlsx", skip = 3, col_names = FALSE)
colnames(r75)[1:13] <- c("Event", "Code", "CaseType", "Total",
                          "GoodsTotal", "NatRes", "Construction",
                          "Manufacturing", "ServiceTotal",
                          "TradeTransUtil", "Information",
                          "Financial", "ProfBusiness")

# Extract same level fall DAFW row
fall_row <- r75[r75$Event == "Slip, trip, stumble or fall on same level" &
                r75$CaseType == "DAFW", ]

# Build analysis dataset
industry_data <- data.frame(
  Industry = c(
    "Finance and Insurance",
    "Information",
    "Professional & Business Services",
    "Construction",
    "Manufacturing",
    "Natural Resources & Mining",
    "Trade, Transportation & Utilities"
  ),
  Category = c(
    "Office", "Office", "Office",
    "Non Office", "Non Office", "Non Office", "Non Office"
  ),
  TRC_Rate = c(
    t1$TRC[t1$NAICS == "52" & !is.na(t1$NAICS)],
    t1$TRC[t1$NAICS == "51" & !is.na(t1$NAICS)],
    t1$TRC[trimws(t1$Industry) == "Professional and business services"][1],
    t1$TRC[t1$NAICS == "23" & !is.na(t1$NAICS)],
    t1$TRC[t1$NAICS == "31-33" & !is.na(t1$NAICS)],
    t1$TRC[grepl("Natural resources and mining", t1$Industry)][1],
    t1$TRC[grepl("Trade, transportation, and utilities", t1$Industry)][1]
  ),
  Fall_Rate = as.numeric(c(
    fall_row$Financial,
    fall_row$Information,
    fall_row$ProfBusiness,
    fall_row$Construction,
    fall_row$Manufacturing,
    fall_row$NatRes,
    fall_row$TradeTransUtil
  ))
)
```

@tbl-summary shows overall injury rates and same level fall rates for each industry sector.
Office industries have noticeably lower rates across both measures compared to Non Office
industries.

```{r}
#| label: tbl-summary
#| tbl-cap: "TRC rates (per 100 FTE) and same level fall DAFW rates (per 10,000 FTE) by industry. Source: BLS SOII [@IIFDatabasesUS]."
#| echo: false

kable(industry_data,
      col.names = c("Industry", "Category", "TRC Rate", "Same Level Fall DAFW Rate"),
      digits = 1, align = c("l","c","c","c")) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE) |>
  row_spec(1:3, background = "lightblue") |>
  row_spec(4:7, background = "salmon")
```

---

## Analysis

::: callout-note

A bit abrupt -- explain how this works and what the goal is before you do the test, then interpret the results.

:::

A two-sample t-test was used to test whether office and Non Office industries differ
in their same level fall DAFW rates.

**Ho:** Mean same level fall rate is equal between office and Non Office industries.  
**Ha:** Mean same level fall rate differs between the two groups.

```{r}
#| label: tbl-ttest
#| tbl-cap: "Two-sample t-test results for same level fall DAFW rates (per 10,000 FTE) by group."
#| echo: false

office    <- industry_data$Fall_Rate[industry_data$Category == "Office"]
nonoffice <- industry_data$Fall_Rate[industry_data$Category == "Non Office"]

result <- t.test(office, nonoffice, var.equal = FALSE)

data.frame(
  Group   = c("Office", "Non Office"),
  Mean    = c(round(mean(office), 1), round(mean(nonoffice), 1)),
  SD      = c(round(sd(office), 1), round(sd(nonoffice), 1)),
  t       = c(round(result$statistic, 2), ""),
  df      = c(round(result$parameter, 1), ""),
  p_value = c(round(result$p.value, 3), ""),
  CI      = c(paste0("[", round(result$conf.int[1], 2), ", ",
                     round(result$conf.int[2], 2), "]"),"")
) |>
  kable(col.names = c("Group", "Mean", "SD", "t", "df", "p-value", "95% CI"),
        align = c("l","c","c","c","c","c","c"),
        na = "") |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)
```

The two-sample t-test showed a statistically significant difference in same level fall rates between office and non office workers, t(3.8) = −3.87, p = 0.020, and a 95% CI [−16.64, −1.81]. Office workers had a significantly lower mean same level fall rate (6.5 per 10,000 FTE) compared to non office workers (15.7 per 10,000 FTE). These results indicate that office workers experience significantly fewer same level falls than non office workers, thus the safety officer’s claim that office workers are at a higher risk of injury is
false.

```{r}
#| label: fig-falls
#| fig-cap: "Same Level Fall DAFW Rates By Industry (per 10,000 FTE). Source: BLS SOII Table R75 [@IIFDatabasesUS]."
#| echo: false

par(mar = c(4, 12, 2, 2))

barplot(industry_data$Fall_Rate,
        names.arg = industry_data$Industry,
        horiz = TRUE,
        las = 1,
        xlab = "Same Level Fall DAFW Rate (per 10,000 FTE)",
        col = ifelse(industry_data$Category == "Office", "lightblue", "salmon"),
        cex.names = 0.7)

legend("bottomright",
       legend = c("Office", "Non Office"),
       fill = c("lightblue", "salmon"))
```
