---
title: "Results"
---

# Draft: Results {#sec-results}

```{r}
#| label: setup
#| echo: false
#| message: false
#| warning: false

library(readxl)
library(knitr)
library(kableExtra)

t1 <- read_excel("Table1.xlsx", skip = 5, col_names = FALSE)
colnames(t1) <- c("Industry", "NAICS", "TRC", "DART", "DAFW", "DJTR", "Other")
t1$TRC <- suppressWarnings(as.numeric(t1$TRC))

r75 <- read_excel("TableR75.xlsx", skip = 3, col_names = FALSE)
colnames(r75)[1:14] <- c("Event", "Code", "CaseType", "Total",
                          "GoodsTotal", "NatRes", "Construction",
                          "Manufacturing", "ServiceTotal",
                          "TradeTransUtil", "Information",
                          "Financial", "ProfBusiness", "EdHealth")

fall_row <- r75[r75$Event == "Slip, trip, stumble or fall on same level" &
                r75$CaseType == "DAFW", ]

industry_data <- data.frame(
  Industry = c(
    "Finance and Insurance",
    "Information",
    "Professional & Business Services",
    "Construction",
    "Manufacturing",
    "Natural Resources & Mining",
    "Trade, Transportation & Utilities"
  ),
  Category = c(
    "Office", "Office", "Office",
    "Non-Office", "Non-Office", "Non-Office", "Non-Office"
  ),
  TRC_Rate = c(
    t1$TRC[t1$NAICS == "52" & !is.na(t1$NAICS)],
    t1$TRC[t1$NAICS == "51" & !is.na(t1$NAICS)],
    t1$TRC[trimws(t1$Industry) == "Professional and business services"][1],
    t1$TRC[t1$NAICS == "23" & !is.na(t1$NAICS)],
    t1$TRC[t1$NAICS == "31-33" & !is.na(t1$NAICS)],
    t1$TRC[grepl("Natural resources and mining", t1$Industry)][1],
    t1$TRC[grepl("Trade, transportation, and utilities", t1$Industry)][1]
  ),
  Fall_Rate = as.numeric(c(
    fall_row$Financial,
    fall_row$Information,
    fall_row$ProfBusiness,
    fall_row$Construction,
    fall_row$Manufacturing,
    fall_row$NatRes,
    fall_row$TradeTransUtil
  ))
)

office    <- industry_data$Fall_Rate[industry_data$Category == "Office"]
nonoffice <- industry_data$Fall_Rate[industry_data$Category == "Non-Office"]
result    <- t.test(office, nonoffice, var.equal = FALSE)
```

## Descriptive Statistics

@tbl-summary shows overall injury rates and same-level fall rates for each industry sector.
Office industries have noticeably lower rates across both measures compared to non-office
industries.

```{r}
#| label: tbl-summary
#| tbl-cap: "TRC rates (per 100 FTE) and same-level fall DAFW rates (per 10,000 FTE) by industry. Source: BLS SOII [@IIFDatabasesUS]."
#| echo: false

kable(industry_data,
      col.names = c("Industry", "Category", "TRC Rate", "Same-Level Fall DAFW Rate"),
      digits = 1, align = c("l","c","c","c")) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE) |>
  row_spec(1:3, background = "#add8e6") |>
  row_spec(4:7, background = "#fa8072")
```

## Analysis

To formally evaluate the safety officer's claim, same-level fall DAFW rates were compared
between office and non-office industries using a two-sample Welch t-test. This test is
appropriate here because we are comparing the means of two independent groups and do not
assume equal variances between them. The goal is to determine whether any observed
difference in fall rates between office and non-office industries is statistically
significant or likely due to chance.

**Ho:** Mean same-level fall rate is equal between office and non-office industries.  
**Ha:** Mean same-level fall rate differs between the two groups.

```{r}
#| label: tbl-ttest
#| tbl-cap: "Two-sample Welch t-test results for same-level fall DAFW rates (per 10,000 FTE) by group."
#| echo: false

data.frame(
  Group   = c("Office", "Non-Office"),
  Mean    = c(round(mean(office), 1),      round(mean(nonoffice), 1)),
  SD      = c(round(sd(office), 1),        round(sd(nonoffice), 1)),
  t       = c(round(result$statistic, 2),  NA),
  df      = c(round(result$parameter, 1),  NA),
  p_value = c(round(result$p.value, 3),    NA),
  CI      = c(paste0("[", round(result$conf.int[1], 2), ", ",
                     round(result$conf.int[2], 2), "]"), NA)
) |>
  kable(col.names = c("Group", "Mean", "SD", "t", "df", "p-value", "95% CI"),
        align = c("l","c","c","c","c","c","c"),
        na = "") |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)
```

The results show a statistically significant difference in same-level fall rates between
office and non-office industries
(t(`r round(result$parameter, 1)`) = `r round(result$statistic, 2)`,
p = `r round(result$p.value, 3)`,
95% CI [`r round(result$conf.int[1], 2)`, `r round(result$conf.int[2], 2)`]).
Office industries averaged `r round(mean(office), 1)` same-level fall cases per 10,000
FTE workers, compared to `r round(mean(nonoffice), 1)` for non-office industries.
These findings do not support the safety officer's claim — office workers experience
significantly *fewer* same-level fall injuries than their non-office counterparts.

```{r}
#| label: fig-falls
#| fig-cap: "Same-level fall DAFW rates by industry (per 10,000 FTE). Source: BLS SOII Table R75 [@IIFDatabasesUS]."
#| echo: false

par(mar = c(4, 12, 2, 2))

barplot(industry_data$Fall_Rate,
        names.arg = industry_data$Industry,
        horiz = TRUE,
        las = 1,
        xlab = "Same-Level Fall DAFW Rate (per 10,000 FTE)",
        col = ifelse(industry_data$Category == "Office", "#add8e6", "#fa8072"),
        cex.names = 0.7)

legend("bottomright",
       legend = c("Office", "Non-Office"),
       fill = c("#add8e6", "#fa8072"))
```