---
title: "Office vs. Non Office Fall Injuries"
subtitle: "Are Stronger Office Safety Policies Warranted?"
author: "Ty Hansen"
format: revealjs
bibliography: references.bib
---

## Background

- ABC Corp operates across both office and industrial environments
- Our safety officer raised concern after a recent article claimed office workers
  are more likely to be injured through falls than non office workers
- **Question:** Should ABC Corp implement stronger safety policies for office staff?

## Data

Data comes from the BLS Survey of Occupational Injuries and Illnesses (SOII) [@IIFDatabasesUS]

Two tables used:

- **Table 1** — Total recordable case (TRC) rates by industry, 2024
  - Per 100 full time equivalent (FTE) workers
- **Table R75** — Days away from work (DAFW) fall rates by industry division, 2023–2024
  - Per 10,000 FTE workers

Industries classified as office or non office based on whether work is primarily
desk-based (NAICS)

## Industry Classification

| Office | Non Office |
|---|---|
| Finance and Insurance | Construction |
| Information | Manufacturing |
| Professional & Business Services | Natural Resources & Mining |
| | Trade, Transportation & Utilities |

## Methods

- Compared same level fall DAFW rates between office and non office industries
- Used a **two-sample t-test** to determine whether differences are statistically
  significant
- Also compared overall TRC rates across groups

**Ho:** Mean same level fall rate is equal between office and non office industries  
**Ha:** Mean same level fall rate differs between the two groups

## Overall Injury Rates

```{r}
#| echo: false
#| message: false
#| warning: false

library(readxl)
library(knitr)
library(kableExtra)

t1 <- read_excel("Table1.xlsx", skip = 5, col_names = FALSE)
colnames(t1) <- c("Industry", "NAICS", "TRC", "DART", "DAFW", "DJTR", "Other")
t1$TRC <- suppressWarnings(as.numeric(t1$TRC))

r75 <- read_excel("TableR75.xlsx", skip = 3, col_names = FALSE)
colnames(r75)[1:14] <- c("Event", "Code", "CaseType", "Total",
                          "GoodsTotal", "NatRes", "Construction",
                          "Manufacturing", "ServiceTotal",
                          "TradeTransUtil", "Information",
                          "Financial", "ProfBusiness", "EdHealth")

fall_row <- r75[r75$Event == "Slip, trip, stumble or fall on same level" &
                r75$CaseType == "DAFW", ]

industry_data <- data.frame(
  Industry = c(
    "Finance and Insurance", "Information",
    "Professional & Business Services",
    "Construction", "Manufacturing",
    "Natural Resources & Mining",
    "Trade, Transportation & Utilities"
  ),
  Category = c(
    "Office", "Office", "Office",
    "Non Office", "Non Office", "Non Office", "Non Office"
  ),
  TRC_Rate = c(
    t1$TRC[t1$NAICS == "52" & !is.na(t1$NAICS)],
    t1$TRC[t1$NAICS == "51" & !is.na(t1$NAICS)],
    t1$TRC[trimws(t1$Industry) == "Professional and business services"][1],
    t1$TRC[t1$NAICS == "23" & !is.na(t1$NAICS)],
    t1$TRC[t1$NAICS == "31-33" & !is.na(t1$NAICS)],
    t1$TRC[grepl("Natural resources and mining", t1$Industry)][1],
    t1$TRC[grepl("Trade, transportation, and utilities", t1$Industry)][1]
  ),
  Fall_Rate = as.numeric(c(
    fall_row$Financial, fall_row$Information, fall_row$ProfBusiness,
    fall_row$Construction, fall_row$Manufacturing,
    fall_row$NatRes, fall_row$TradeTransUtil
  ))
)

office    <- industry_data$Fall_Rate[industry_data$Category == "Office"]
nonoffice <- industry_data$Fall_Rate[industry_data$Category == "Non Office"]
result    <- t.test(office, nonoffice, var.equal = FALSE)

kable(industry_data,
      col.names = c("Industry", "Category", "TRC Rate", "Same-Level Fall DAFW Rate"),
      digits = 1, align = c("l","c","c","c")) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = TRUE,
                font_size = 18) |>
  row_spec(1:3, background = "lightblue") |>
  row_spec(4:7, background = "salmon")
```

## Fall Rates by Industry

```{r}
#| echo: false

par(mar = c(4, 12, 2, 2))

barplot(industry_data$Fall_Rate,
        names.arg = industry_data$Industry,
        horiz = TRUE,
        las = 1,
        xlab = "Same-Level Fall DAFW Rate (per 10,000 FTE)",
        col = ifelse(industry_data$Category == "Office", "lightblue", "salmon"),
        cex.names = 0.7)

legend("bottomright",
       legend = c("Office", "Non Office"),
       fill = c("lightblue", "salmon"))
```

## Results

```{r}
#| echo: false

data.frame(
  Group   = c("Office", "Non Office"),
  Mean    = c(round(mean(office), 1),     round(mean(nonoffice), 1)),
  SD      = c(round(sd(office), 1),       round(sd(nonoffice), 1)),
  t       = c(round(result$statistic, 2), NA),
  df      = c(round(result$parameter, 1), NA),
  p_value = c(round(result$p.value, 3),   NA),
  CI      = c(paste0("[", round(result$conf.int[1], 2), ", ",
                     round(result$conf.int[2], 2), "]"), NA)
) |>
  kable(col.names = c("Group", "Mean", "SD", "t", "df", "p-value", "95% CI"),
        align = c("l","c","c","c","c","c","c"),
        na = "") |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = TRUE,
                font_size = 20)
```

Office industries averaged `r round(mean(office), 1)` same level fall cases per 10,000
FTE workers vs. `r round(mean(nonoffice), 1)` for non office industries,
a statistically significant difference (p = `r round(result$p.value, 3)`)

## Limitations

- **Low statistical power** — only 7 industry divisions compared
- **Employer-reported data** — underreporting is a known limitation of SOII
- **Industry-level classification** — office vs. non office is a simplification;
  many industries contain both types of workers
- Future analysis using **occupation level data** would allow for a more precise comparison

## Recommendation

::: {.callout-important}
The data does **not** support implementing stronger fall safety policies for office workers
:::

- Safety resources should be directed toward **industrial and manufacturing operations**
  where injury risk is substantially higher
- Basic office precautions (cable management, lighting, non slip flooring) remain
  worthwhile but do not require significant new investment
- Future work should examine specific office roles and the impact of hybrid work on
  injury patterns

## Thank You

**Questions?**

Data source: BLS Survey of Occupational Injuries and Illnesses [@IIFDatabasesUS]